Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-21 Paper/ms.tex
Eccentricity
Gliese 581 in abstract

\begin{abstract}
Inferring the number of planets $N$ in an exoplanetary system from radial velocity
(RV) data is a challenging task. Typically, the posterior distribution for the
planet parameters is multimodal and may have other awkward features. In
addition, when $N$ is unknown, the marginal likelihood (or evidence), as a
function of $N$, is required. In this paper we propose an alternative
approach using a trans-dimensional Markov Chain Monte Carlo method within
Nested Sampling. The posterior distribution for $N$ can be obtained with a
single run, which takes $\sim$ 15 minutes on a typical modern desktop computer.
We apply the method to $\nu$ Oph and Gliese 581, finding moderate evidence
(posterior probability of existence = 70\%) for a third planet around
$\nu$ Oph with an orbital period of 75.7 $\pm$ 1.8 days. 
\end{abstract}

@@

>>>>

\begin{abstract}
Inferring the number of planets $N$ in an exoplanetary system from radial velocity
(RV) data is a challenging task. Typically, the posterior distribution for the
planet parameters, such as orbital periods,
is multimodal and may have other awkward features. In
addition, when $N$ is unknown, the marginal likelihood (or evidence), as a
function of $N$, is required. In this paper we propose an alternative
approach using a trans-dimensional Markov Chain Monte Carlo method within
Nested Sampling. The posterior distribution for $N$ can be obtained with a
single run, which takes $\sim$ 15 minutes on a typical modern desktop computer.
We apply the method to $\nu$ Oph and Gliese 581, finding moderate evidence
(posterior probability of existence = 70\%) for a third planet around
$\nu$ Oph with an orbital period of 75.7 $\pm$ 1.8 days. The results also
suggest Gliese 581 hosts many (7-15) planets (or causes of other periodic
signals), but only four have well determined orbital periods. 
\end{abstract}

@@

Although we parameterise the eccentricity using the initial velocity $v$,
the standard eccentricity $\epsilon$ can be recovered using the relation
$\epsilon = 1 - v^2$.
